\textbf{EECS 340: Assignment 5}

### 2020-04-07 assignment_5/article.tex
✨ Add Problem 2(a) response.

\paragraph{(v)}
We have $T(n) = \Theta(mn)$. A matrix of $m \cdot n$ is filled when two strings are listing their possible reductions of chars, thus there are $\Theta(mn)$ subproblems. Each subproblem takes $\Theta(1)$ to execute.\\
$\Longrightarrow T(n) =  \Theta(mn) \cdot \Theta(1) =  \Theta(mn)$

@@

>>>>

\paragraph{(v)}
We have $T(n) = \Theta(mn)$. A matrix of $m \cdot n$ is filled when two strings are listing their possible reductions of chars, thus there are $\Theta(mn)$ subproblems. Each subproblem takes $\Theta(1)$ to execute as all edit options cost the same.\\
$\Longrightarrow T(n) =  \Theta(mn) \cdot \Theta(1) =  \Theta(mn)$

@@

\subsection{(a)}
\begin{proof}
Suppose we have $r_{ij}$ for the optimal exchange between currencies $i \to j$, with an substructure of $r_{ij} = r_{ik} \cdot r_{kj}$ (for $k \in [i,j]$). We want to show both $r_{ik}$ and $r_{kj}$ must be the optimal exchange between currencies $i \to k$ and $k \to j$.

Without lost of generality, assume we have $r'_{ik}$ where $r'_{ik} > r_{ik}$, then there must be $r'_{ik} \cdot r_{kj} > r_{ij}$. Which suggest $r_{ij}$ is no longer optimal for the exchange between currencies $i \to j$ and the assumption is void. Thus, we proved substructure $r_{ik}$ must be at its optimal structure by contradiction. And an optimal $r_{ij}$ is only obtainable with optimal substcutures.
\end{proof}
